\chapter{Web Service Implementations}
\textcolor{red}{FROM HUBERT:\\
"The first subsection of this section should explain the data structures used and contain class diagrams providing an overview over for the used data structures for both RESTful and SOAP/BPEL Web services The airline- and hotel reservation services mentioned in Sect. 2.3.1 and 2.3.2 should have a short description of what they do and how they are implemented. What were the design decisions involved?
For example, which binding style was used and why (e.g. document/literal)?
The next section should explain the BPEL process and how it works. It should be possible to
understand the implementation of the BPEL process from your text. Explain the design decisions you have made, e.g. what are the port types, operations, which binding style was used and why, . . . .
The last section should explain your RESTful implementation. In particular\\
• What have you chosen to be represented as resources and why\\
• How are activities of the business process mapped to HTTP verbs, like GET, PUT, POST, DELETE, . . . .\\
• How the business logic is implemented\\
• Which representations you have chosen and why"\\
Input relevant tex files regarding the implementations here...
Please create ONE tex file for each data structure used (if more than one is used).}

\input{Chapters/Web_Service_Implementations/Data_Structures_Used/data_structures_used.tex}
\input{Chapters/Web_Service_Implementations/Reservation_Services/reservation_services.tex}
\input{Chapters/Web_Service_Implementations/Bpel_Implementation/bpel_implementation.tex}
\input{Chapters/Web_Service_Implementations/Restful_Implementation/restful_implementation.tex}
